Blowship - Untraceable Instantaneous Message Transfer via a Central Server

### 2014-03-15 paper.tex
LAMBERT

\subsection{Solutions}
To begin solving these problems, we will need to change the protocol so that any non-Penguin peer will always wait until it can send \textbf{two or more messages simultaneously}. This is equivilant to turning each peer into a 2-threshold mix. \cite{TODO}

@@

\subsection{The Fort} Assuming the set $S$ of peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is some chance that all chosen peers are colluding with Surge $(R \subset S)$ and so Alice's identity is completely compromised $(P_{AB} = 1$ and $S = 0)$.

@@

The chance Surge can tell with probability greater than $\gamma$ that Alice and Bob are talking to each other, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Fort members as peers.

Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability $\sum\limits_{i=x}^n\phi^ifdas$ where 
\\ $P_{AB} = 2^{-(n - x)} = 2^{-(\log(N) - x)} = \gamma$
\\ $ \Rightarrow x = 2^{\log\log(N)/\gamma}$

\begin{figure}[ht]
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    $\phi$ & N & $E[P_{AB}]$ & x & n & $p(P_{AB} > 0.5)$ \\\hline
    0.5 & 1000 & 0.031 & 4 & 10 & 0.12\\
    0.5 & 10000 & 0.01 & 4 & 14 & 0.12\\
    0.5 & 100000 & 0.003 & 5 & 17 & 0.06\\
    \hline
  \end{tabular}
  \caption{Table 42.42 - Probabilities things are bad}
\end{figure}

While less than ideal, this is not unreasonable. The chance that Surge, having $50\%$ of 1000 peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is only $12\%$.

@@

Lying about who's online - If you want to send a message to a real node ``B'' but B is not listed as online, you won't send a message. However, if he lists ``B'' as online, ``B'' can be used to route messages validly by everyone.

@@

\subsection{Peer Discovery}
Unfortunately, if peers discover eachother through Surge, he can ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).

@@

>>>>

\section{Improved Protocol}
To begin solving these problems, we will need to change the protocol so that any non-Penguin peer will always wait until it can send \textbf{two or more messages simultaneously}. This is equivilant to turning each peer into a 2-threshold mix. \cite{TODO}

@@

\subsection{Analysis of a simple message} 
Using this improved pseudo-P2P message system, we will analyze the security of Alice sending a single message to Bob.

Assuming the set $S$ of peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is some chance that all chosen peers are colluding with Surge $(R \subset S)$ and so Alice's identity is completely compromised $(P_{AB} = 1$ and $S = 0)$.

@@

The chance Surge can tell with probability greater than $\gamma$ that Alice and Bob are talking to each other, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Fort members as peers. 
\begin{center}
$\gamma = P_{AB} = 2^{-(n - x)} = 2^{-(\log(N) - x)}$
\\ $ \Rightarrow x = log( \gamma ) + n$
\end{center}
Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability:
\begin{center}
 $p(P_{AB} > \gamma) = \mathlarger{\sum}\limits_{i=\log(\gamma) + n}^n {n \choose i} \phi^i (1 - \phi )^{n-i}$

\end{center}

Intuitively, Alice would be in an anonymity set of size 2 when $\gamma = 0.5$. This happens when all but one nodes are compromised: $x = log( 0.5 ) + n = n - 1$.

\begin{figure}[ht]
  \small
  \begin{tabular}{| l | l | l | l | l | l |}

    \hline
    $\phi$ & N & n & x & $E[P_{AB}]$ & $p(P_{AB} > 0.5)$ \\\hline
    0.8 & 1000 & 10 & 9 & 0.031 & 0.38\\
    0.8 & 10000 & 14 & 13 & 0.010 & 0.20\\
    0.8 & 100000 & 17 & 16 & 0.003 & 0.12\\
    \hline
  \end{tabular}
  \caption{Table 42.42 - Probabilities things are bad}
\end{figure}

\newpage
As seen in table 42.42, the chance that Surge, having $80\%$ of 10000 peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is $20\%$. If Surge believes $P_{AB} = 0.5$ given 10000 peers, then the probability distribution size $S = 1.93$.

If this level of security is unacceptable, the length of the circuit can be chosen based on an estimate of $\phi$ and an acceptable $p(P_{AB} > \gamma)$. Assuming $\gamma = 0.5$, then 
\begin{center}
$p(P_{AB} > 0.5)$ = $n\phi^{n-1} (1 - \phi ) + \phi^n $
\end{center}

Although n is difficult to solve for directly (requiring the Lambert W equation), a we give a graph for $n$ and $\phi$ given $\gamma = 0.5$:

\includegraphics*[width=\linewidth]{gamma5graph.png}

Given this graph it's clear that if the network is believed to be widely compromised, security can be made up for by choosing longer circuits. Although $\phi = 0.8$ makes $n = 10$ an unviable choice, at a circuit length of $n=20$ having $\phi = 0.8$ hardly affects the security.

@@

@@

\subsection{Peer Discovery}
Unfortunately, if peers discover eachother through Surge, he could ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).

@@

We solve this problem as follows:
